---
title: "Tips and tricks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tips and tricks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev.args = list(png = list(type = "cairo-png"))
)
```

```{r setup}
library(ggoutlines)

lineplot <- ggplot(economics_long, aes(date, value01, colour = variable))
```

## Stroke colour

Any colour scale is also applicable to the `stroke_colour` aesthetic, if the `aesthetics` argument of the scale includes `"stroke_colour"`. While this generally works fine for legend guides, the `guide_colourbar()` guide also needs an adjusted `available_aes`.

```{r}
lineplot + 
  geom_line_outline(aes(stroke_colour = value01)) +
  scale_colour_viridis_c(
    aesthetics = "stroke_colour",
    guide = guide_colourbar(available_aes = "stroke_colour")
  )
```



Matching the stroke colour automatically to the currently active theme:

```{r}
lineplot +
  geom_line_outline(
    stroke_colour = theme_get()$panel.background$fill,
    stroke_linewidth = 2
  )
```

Making stroke colour a darker version of the normal colour.

```{r}
# Can save as variable to re-use in multiple plots
dark_outline <- aes(stroke_colour = after_scale(
  farver::add_to_channel(colour, "l", -30, "hcl"))
)

lineplot +
  geom_path_outline(
    aes(,,!!!dark_outline)
  )
```
